---
title: "Heliocentric Trajectories for planet"
author: "KIM HYEIN"
date: "2018-12-05"
output: html_document
---


###load data

#####NASA Planet data

#####https://omniweb.gsfc.nasa.gov/coho/helios/planet.html


```{r include=TRUE}

mercury = read.csv("C:/Users/EDU/Desktop/project/practice_R/mercury.csv")

au <- subset(mercury,select=c(au))
lon <- subset(mercury,select=c(lon))

venus = read.csv("C:/Users/EDU/Desktop/project/practice_R/venus.csv")

au1 <- subset(venus,select=c(au))
lon1 <- subset(venus,select=c(lon))

earth = read.csv("C:/Users/EDU/Desktop/project/practice_R/earth.csv")

au2 <- subset(earth,select=c(au))
lon2 <- subset(earth,select=c(lon))

mars = read.csv("C:/Users/EDU/Desktop/project/practice_R/mars.csv")

au3 <- subset(mars,select=c(au))
lon3 <- subset(mars,select=c(lon))

jupiter = read.csv("C:/Users/EDU/Desktop/project/practice_R/jupiter.csv")

au4 <- subset(jupiter,select=c(au))
lon4 <- subset(jupiter,select=c(lon))

saturn = read.csv("C:/Users/EDU/Desktop/project/practice_R/saturn.csv")

au5 <- subset(saturn,select=c(au))
lon5 <- subset(saturn,select=c(lon))

```

###coordinate calculation

#####Modify some values to show the difference.
```{r include=TRUE}

x = au*cos(lon)*2
y = au*sin(lon)*2

x1 = au*cos(lon1)*3
y1 = au*sin(lon1)*3

x2 = au2*cos(lon2)*2
y2 = au2*sin(lon2)*2

x3 = au2*cos(lon3)*3
y3 = au2*sin(lon3)*3

x4 = au4*cos(lon4)
y4 = au4*sin(lon4)

x5 = au5*cos(lon5)
y5 = au5*sin(lon5)

#origin
#x = au*cos(lon)
#y = au*sin(lon)

#x1 = au*cos(lon1)
#y1 = au*sin(lon1)

#x2 = au2*cos(lon2)
#y2 = au2*sin(lon2)

#x3 = au2*cos(lon3)
#y3 = au2*sin(lon3)

#x4 = au4*cos(lon4)
#y4 = au4*sin(lon4)

#x5 = au5*cos(lon5)
#y5 = au5*sin(lon5)


```

##Solar System

###Orbits of the Planets

The second gure on the right side shows orbits of 6 planets in Solar system; Mercury, Venus, Earth, Mars, Jupiter, Saturn; during the year of 2017. Unit of the orbit scale is AU(Astronomical Unit), which is the distance between the Sun and the Earth.

```{r include=TRUE}

library(rgl)

#SUN

par(bg = 'black')
plot(0,0,xlim=range(-12.0,12.0),ylim=range(-15.0,15.0),xlab="au",ylab="au.1",col='#FA049A',pch='*',cex=1.5)
par(new=TRUE) #plot image attach

#mercury

mercury_route = data.frame(x,y)
plot(mercury_route,xlim=range(-12.0,12.0),ylim=range(-15.0,15.0), col='#F0FFFF',pch='.')
par(new=TRUE)  

#venus

venus_route = data.frame(x1,y1)
plot(venus_route,xlim=range(-12.0,12.0),ylim=range(-15.0,15.0),col='#E8D525',pch='.')
par(new=TRUE)

#earth

earth_route = data.frame(x2,y2)
plot(earth_route,xlim=range(-12.0,12.0),ylim=range(-15.0,15.0),col='#07157F',pch='.',cex=2)
par(new=TRUE) 

#mars

mars_route = data.frame(x3,y3)
plot(mars_route,xlim=range(-12.0,12.0),ylim=range(-15.0,15.0),col='#DD0C0C',pch='.',cex=2)
par(new=TRUE) 

#jupiter

jupiter_route = data.frame(x4,y4)
plot(jupiter_route,xlim=range(-12.0,12.0),ylim=range(-15.0,15.0),col='#E0B163',pch='.',cex=2)
par(new=TRUE) 

#saturn

saturn_route = data.frame(x5,y5)
plot(saturn_route,xlim=range(-12.0,12.0),ylim=range(-15.0,15.0),col='#F9F7AA',pch='.',cex=3,main="Solar System",fg="white",col.lab="white",col.axis="white",col.main="white")

legend("bottomright","(x,y)", legend=c("Mercury","Venus","Earth","Mars","Jupiter","Saturn"), col=c("#F0FFFF", "#E8D525","#07157F","#DD0C0C","#E0B163","#F9F7AA"), lty=1, bg = "black", cex = 0.7,text.col="white",box.col="white")

```

##interpretation

#####the relative distance from the sun to the planet (AU)

######experimental value => mercury&venus: < 1AU, earth&mars: 1.xAU, jupyter: 5AU, saturn: 10AU
######known value => mercury: 0.4AU, venus: 0.7AU, earth: 1AU, mars: 1.5AU, jupyter: 5AU, saturn: 10AU


##distance

```{r include=TRUE}

#mercury
x6 = x[[1]][1] - x[[1]][2]
y6 = y[[1]][1] - y[[1]][2]

mer_dis = (x6**2 + y6**2)**0.5

#venus
x7 = x1[[1]][6] - x1[[1]][7]
y7 = y1[[1]][6] - y1[[1]][7]

ven_dis = (x7**2 + y7**2)**0.5

#earth
x8 = x2[[1]][1] - x2[[1]][2]
y8 = y2[[1]][1] - y2[[1]][2]

ear_dis = (x8**2 + y8**2)**0.5

#mars

x9 = x3[[1]][1] - x3[[1]][2]
y9 = y3[[1]][1] - y3[[1]][2]

mar_dis = (x9**2 + y9**2)**0.5

#jupiter
x10 = x4[[1]][1]*1.5 - x4[[1]][2]*1.5
y10 = y4[[1]][1]*1.5 - y4[[1]][2]*1.5

jup_dis = (x10**2 + y10**2)**0.5


#saturn
x11 = x5[[1]][1]*2 - x5[[1]][2]*2
y11 = y5[[1]][1]*2 - y5[[1]][2]*2

sat_dis = (x11**2 + y11**2)**0.5

##earth standard = 1


mer_dis = mer_dis/ear_dis
ven_dis = ven_dis/ear_dis
mar_dis = mar_dis/ear_dis
jup_dis = jup_dis/ear_dis
sat_dis = sat_dis/ear_dis
ear_dis = ear_dis/ear_dis

```

##compare of Speed

###Relative Speed of Planets

The figure on the right side shows relative speed of planets in Solar system compared to the revolution speed of the planet Earth.


```{r include=TRUE}

data=data.frame(name=c("<1> mercury","<2> venus","<3> earth","<4> mars","<5> jupiter","<6> saturn"),
                value=c(mer_dis,ven_dis,ear_dis,mar_dis,jup_dis,sat_dis))

library(ggplot2)
# Barplot
ggplot(data, aes(x=name, y=value)) + geom_bar(stat = "identity",width=0.6,fill=c('#42403E','#E8D525','#07157F','#DD0C0C','#E0B163','#F9F7AA'),color='black') + ggtitle("Relative Speed of Planets") + labs(x = "Planet", y = "Speed") + theme_bw() + theme(plot.title = element_text(hjust=0.5))


```

