---
title: "R basic"
author: "KimHyein"
date: "2018/12/03"
output:
  html_document: default
  pdf_document: default
---

```{r include=FALSE}

#install.packages('ggmap')
#install.packages("ggplot2")
#install.packages('rgl')

```

##1. Vector/Array

Arrays can store only data type.

### [Including Code]

```{r include=TRUE}

a = c(1,3,5,7,9)
b = c('Kim','Lee','Michael','Lee')

#Get the first element
a[1]

a[2:5]

length(a)

sum(a)

mean(a)

a+1

#Compare elements
a==3

#Find the index
which(a==5)

#Get the element with an index
a[which(a==5)]

which(b=='Lee')

#Count the matched
length(which(b=='Lee'))
```



##2. List

A list is an R structure that may contain objects of any other types, including other lists.
List items need to be pointed by [[index]] (double square brackets)
'List' can make tree-like data

### [Including Code]


```{r include=TRUE}
#List
L = list(ids=1:5, whos=c('Kim','Lee','Choi'))

names(L)

L[[1]]

L$ids

L$whos

L$whos[1]

L[[1]][5]

```



##3. DataFrame

A data frame is a table or a two-dimensional array-like structure in which each column contains values of one variable and each row contains one set of values from each column

### [Including Code]

```{r include=TRUE}
last_name = c('lee','kim','choi','park','lee')
age = c(24,30,50,34,12)
gender = c('M','F','M','M','M')

last_name
age
gender

#create dataframe
person = data.frame(last_name,age,gender)
person


person$last_name
person$age
person$gender

person[3,2]
person[3,1:3]
person[3,]
person[3,]$age
person[3,'age']

person$last_name=='choi'
which(person$last_name=='choi')
person[which(person$last_name=='choi'),]

person$age==12
which(person$age==12)
person[which(person$age==12),]

person[which(person$age>=30),]

person[which(person$gender=='M'),]

#nrow => row count
nrow(person[which(person$gender=='M'),])

#length => column count
length(person[which(person$gender=='M'),])

person[which(person$gender=='M'& person$age<=30),]
person[which(person$gender=='M'| person$age<=30),]

```



##4. Matrix

### [Including Code]

```{r include=TRUE}
matrix(1:12,nrow=3,byrow=FALSE)

matrix(1:12,nrow=3,byrow=TRUE)

A = matrix(1:12,nrow=3,byrow=TRUE)
A
A[2,3]
A[1:2,3:4]
t(A)

```



##5. Json
(Data Expression Sharing)

JSON: JavaScript Object Notation

JSON is a syntax for storing and exchanging data.
JSON is text, written with javascript obect notation.

### [Including Code]


```{r include=TRUE}

item1 = list(name='Lee',age=35)
item2 = list(name='Kim',age=25)
item3 = list(name='Smith',age=40)

members = list(item1,item2,item3)

library(rjson)

toJSON(members)

con = file('test.json')

writeLines(toJSON(members),con)

group = fromJSON(file='test.json')

all.equal(members,group)

```



##6. Function

One of the great strengths of R is the user's ability to add functions. The structure of a function is given below.

myfunction <- function(arg1, arg2, ...){

statements

return(object)

}

### [Including Code]


```{r include=TRUE}

myfunc = function(a,b) {return(a+b)}
myfunc(1,2)

myfunc = function(a,b,c=100) {return(a+b+c)}
myfunc(1,2)
myfunc(1,2,1000)

myfunc = function(a) {if(a==1) TRUE else FALSE}
myfunc
myfunc(1)
myfunc(2)

b = c(1:5)
b

for(i in b) {print(myfunc(i))}

```



##7. Save

save: writes an external representation of R objects to the specified file.

1) save.image(file='.Rdata), save.image() ==> save all
2) save.image(variable, file='variable.Rdata) ==> save variable

### [Including Code]


```{r include=TRUE}

a = c(1:100)
a

save(a,file='a_save.RData')

remove(a)

#>a
#Error: object 'a' not found 

load(file='a_save.RData')
a

```


##8. Apply

returns a vector or array or list of values obtained by applying a function to margins of an array or matrix.

lapply returns a list of the same length as X, each element of which is the result of applying FUN to the corresponding element of X.

apply(X, MARGIN, FUN, ...)

MARGIN: 1-> Row way, 2-> Column way


### [Including Code]


```{r include=TRUE}

x = cbind(x1 = 3,x2 = c(4:1,2:5))
dimnames(x)[[1]] <- letters[1:8]
x

apply(x,1,mean,trim=.2)

apply(x,2,mean,trim=.2)

lapply(c(1:3),function(x) {x+100})


y = cbind(x1 = 3,x2 = c(4:1,2:5))
y

dimnames(y)[[1]] <- letters[1:8]
y

dimnames(y)[[2]] <- letters[9:10]
y

z = c(x1 = 3, x2 = 5)
z

z = cbind(x1 = 3, x2 = 5)
z

z = c(x1 = 3, x2 = c(1:5))
z

z = cbind(x1 =3, x2 = c(1:5))
z

```



##9. Plot

### [Including Code]


```{r include=TRUE}


x = rnorm(100)
y = rnorm(100)
t_data = data.frame(x,y)
plot(t_data$x,t_data$y)

t_data$x
View(t_data)

plot(rnorm(10),type='o',xlab='step',ylab='strength',col='#FF00FF',pch='+',cex=3,main='TITLE')

```

##10. ggPlot

### [Including Code]

```{r include=TRUE}

library(ggplot2)

test_data = data.frame(step=1:100,value=abs(rnorm(100)))
head(test_data)

hist(test_data$value)
ggplot(test_data,aes(x=value))+geom_histogram()

```


##11. 3DPlot

### [Including Code]

```{r include=TRUE}

#0,5,10,,,360
x = seq(0,360,by=5)

#radian value change
y = sin(x*pi/180)

plot(x,y,type='o',pch='+')

library(rgl)

plot3d(rnorm(100),rnorm(100),rnorm(100))
test_data = data.frame(x=rnorm(100),y=rnorm(100),z=rnorm(100))
plot3d(test_data)
head(test_data)


plot3d(NULL,xlab='')
r=10
for (p in seq(0,180,10)) {
  q = seq(0,360,10)
  x = r *sin(p*pi/180)*cos(q*pi/180)
  y = r *sin(p*pi/180)*sin(q*pi/180)
  z = r *cos(p*pi/180)
  points3d(x,y,z)
  lines3d(x,y,z,col='red')
}


```

##12. Map

### [Including Code]

```{r include=TRUE}

library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)

map_data

asia = map_data("world",region=c("South Korea","North Korea"))

g = ggplot(asia,aes(x=long,y=lat,group=group,fill=region)) + 
  geom_polygon(colour="black") +
  scale_fill_brewer(palette="Set1")

plot(g)

head(asia)
tail(asia)

plot(asia[,c('long','lat')])
plot(asia[,c('long','lat')],type='l')
plot(asia[asia$subregion=='Cheju Do',c('long','lat')],type='o')

```

##13. googlemap  [not running]

### [Including Code]

{r include=TRUE}

library(ggmap)
library(ggplot2)
library(maps)
library(mapdata)

g_map = get_map(
  location = c(lon = 127.102773,
               lat = 37.512423),
  color = "color",
  source = "google",
  maptype = "roadmap",
  zoom = 16)

ggmap(g_map,
      extent = "device",
      ylab = "Latitude",
      xlab = "Longitude")

ourPosition = data.frame(lon=127.102773, lat = 37.512423)

ggmap(g_map) + geom_point(data=ourPosition,aes(x=lon,y=lat),
                          shape=9,color='red',size=5) +
              geom_text(data=ourPosition,aes(x=lon,y=(lat)),
              color='red',label='We are here!',vjust=1.8)



>ERROR MASSAGE

cannot open URL 'http://maps.googleapis.com/maps/api/staticmap?center=37.512423,127.102773&zoom=16&size=640x640&scale=2&maptype=roadmap&language=en-EN&sensor=false': HTTP status was '403 Forbidden'Error in download.file(url, destfile = tmp, quiet = !messaging, mode = "wb") : 
  cannot open URL 'http://maps.googleapis.com/maps/api/staticmap?center=37.512423,127.102773&zoom=16&size=640x640&scale=2&maptype=roadmap&language=en-EN&sensor=false'
  


##14. Linear_Regression

### [Including Code]

```{r include=TRUE}

head(airquality)
tail(airquality)
plot(airquality)
res = lm(formula = Ozone ~ Wind, data=airquality)
plot(airquality[,c('Wind','Ozone')],cex=0.3)
abline(res,col='red')

```

##15. Clustering

### [Including Code]

```{r include=TRUE}

num_of_clusters=5
num_of_elements=200

x = sample(1:1000,num_of_elements,replace=F)
y = sample(1:1000,num_of_elements,replace=F)

t_data = data.frame(x=x,y=y)
head(t_data)

plot(x,y,cex=0.1)

res = kmeans(t_data,num_of_clusters)

for (i in 1:num_of_clusters) {
  for (j in which(res$cluster==i)) {
  lines(c(res$centers[i,1],t_data[j,1]),
       c(res$centers[i,2],t_data[j,2]),
       col=i+3)
}
  points(res$centers[i,1],t_data[i,2], col='red',cex=2)

  text(res$centers[i,1],t_data[i,2],labels=paste('center-',i),pos=3,cex=0.7)

}

```
