---
title: "R basic"
author: "KimHyein"
date: "2018/12/03"
output:
  html_document: default
  pdf_document: default
---

##1. Vector/Array

Arrays can store only data type.

### [Including Code]

```{r include=TRUE}

a = c(1,3,5,7,9)
b = c('Kim','Lee','Michael','Lee')

#Get the first element
a[1]

a[2:5]

length(a)

sum(a)

mean(a)

a+1

#Compare elements
a==3

#Find the index
which(a==5)

#Get the element with an index
a[which(a==5)]

which(b=='Lee')

#Count the matched
length(which(b=='Lee'))
```



##2. List

A list is an R structure that may contain objects of any other types, including other lists.
List items need to be pointed by [[index]] (double square brackets)
'List' can make tree-like data

### [Including Code]


```{r include=TRUE}
#List
L = list(ids=1:5, whos=c('Kim','Lee','Choi'))

names(L)

L[[1]]

L$ids

L$whos

L$whos[1]

L[[1]][5]

```



##3. DataFrame

A data frame is a table or a two-dimensional array-like structure in which each column contains values of one variable and each row contains one set of values from each column

### [Including Code]

```{r include=TRUE}
last_name = c('lee','kim','choi','park','lee')
age = c(24,30,50,34,12)
gender = c('M','F','M','M','M')

last_name
age
gender

#create dataframe
person = data.frame(last_name,age,gender)
person


person$last_name
person$age
person$gender

person[3,2]
person[3,1:3]
person[3,]
person[3,]$age
person[3,'age']

person$last_name=='choi'
which(person$last_name=='choi')
person[which(person$last_name=='choi'),]

person$age==12
which(person$age==12)
person[which(person$age==12),]

person[which(person$age>=30),]

person[which(person$gender=='M'),]

#nrow => row count
nrow(person[which(person$gender=='M'),])

#length => column count
length(person[which(person$gender=='M'),])

person[which(person$gender=='M'& person$age<=30),]
person[which(person$gender=='M'| person$age<=30),]

```



##4. Matrix

### [Including Code]

```{r include=TRUE}
matrix(1:12,nrow=3,byrow=FALSE)

matrix(1:12,nrow=3,byrow=TRUE)

A = matrix(1:12,nrow=3,byrow=TRUE)
A
A[2,3]
A[1:2,3:4]
t(A)

```



##5. Json
(Data Expression Sharing)

JSON: JavaScript Object Notation

JSON is a syntax for storing and exchanging data.
JSON is text, written with javascript obect notation.

### [Including Code]


```{r include=TRUE}

item1 = list(name='Lee',age=35)
item2 = list(name='Kim',age=25)
item3 = list(name='Smith',age=40)

members = list(item1,item2,item3)

library(rjson)

toJSON(members)

con = file('test.json')

writeLines(toJSON(members),con)

group = fromJSON(file='test.json')

all.equal(members,group)

```



##6. Function

One of the great strengths of R is the user's ability to add functions. The structure of a function is given below.

myfunction <- function(arg1, arg2, ...){

statements

return(object)

}

### [Including Code]


```{r include=TRUE}

myfunc = function(a,b) {return(a+b)}
myfunc(1,2)

myfunc = function(a,b,c=100) {return(a+b+c)}
myfunc(1,2)
myfunc(1,2,1000)

myfunc = function(a) {if(a==1) TRUE else FALSE}
myfunc
myfunc(1)
myfunc(2)

b = c(1:5)
b

for(i in b) {print(myfunc(i))}

```



##7. Save

save: writes an external representation of R objects to the specified file.

#####1.) save.image(file='.Rdata'), save.image() ==> 작업한 것 모두 저장

#####2.) save(변수명,file='변수명.Rdata') ==> 특정 변수 저장 (재사용 가능)

### [Including Code]


```{r include=TRUE}

a = c(1:100)
a

save(a,file='a_save.RData')

remove(a)

#>a
#Error: object 'a' not found 

load(file='a_save.RData')
a

```


##8. Apply

returns a vector or array or list of values obtained by applying a function to margins of an array or matrix.

lapply returns a list of the same length as X, each element of which is the result of applying FUN to the corresponding element of X.

apply(X, MARGIN, FUN, ...)

MARGIN: 1-> Row way, 2-> Column way


### [Including Code]


```{r include=TRUE}

x = cbind(x1 = 3,x2 = c(4:1,2:5))
dimnames(x)[[1]] <- letters[1:8]
x

apply(x,1,mean,trim=.2)

apply(x,2,mean,trim=.2)

lapply(c(1:3),function(x) {x+100})


y = cbind(x1 = 3,x2 = c(4:1,2:5))
y

dimnames(y)[[1]] <- letters[1:8]
y

dimnames(y)[[2]] <- letters[9:10]
y

z = c(x1 = 3, x2 = 5)
z

z = cbind(x1 = 3, x2 = 5)
z

z = c(x1 = 3, x2 = c(1:5))
z

z = cbind(x1 =3, x2 = c(1:5))
z

```

